Experience Report: Haskell in Computational Biology

### 2012-02-10 mrfy_experience_report.tex
some notes added

@@

@@

We wrote a basic search function in only twenty-five lines of code; as one of 
its parameters we provide a \texttt{SearchStrategy} data type, which we use to 
define specific search techniques. We require a \texttt{SearchStrategy} to 
define four functions: \texttt{mutate}, \texttt{accept}, \texttt{terminate}, 
and \texttt{initialize}; we use the Haskell module system to allow sharing of 
some of these functions between different search strategies. For example, both 
\textit{random mutation hill climb} and \textit{simulated annealing} use the 
same initialize and mutate functions, but very different accept functions. In 
all, we implemented four search strategies: \textit{random mutation hill 
climb}, \textit{simulated annealing}, \textit{multistart simulated annealing}, 
and \textit{genetic algorithm}. We found the implementation of the search 
function and search strategies to be pleasant, and the resulting code to be 
simple and elegant.

>>>>

[insert Viterbi recurrence relations]

@@

[part of Viterbi code]

@@

We wrote a basic search function in only twenty-two lines of code; as one of 
its parameters we provide a \texttt{SearchStrategy} data type, which we use to 
define specific search techniques. We require a \texttt{SearchStrategy} to 
define four functions: \texttt{mutate}, \texttt{accept}, \texttt{terminate}, 
and \texttt{initialize}; we use the Haskell module system to allow sharing of 
some of these functions between different search strategies. For example, both 
\textit{random mutation hill climb} and \textit{simulated annealing} use the 
same initialize and mutate functions, but very different accept functions. In 
all, we implemented four search strategies: \textit{random mutation hill 
climb}, \textit{simulated annealing}, \textit{multistart simulated annealing}, 
and \textit{genetic algorithm}. We found the implementation of the search 
function and search strategies to be pleasant, and the resulting code to be 
simple and elegant.

[listing for search function, and constructor for SearchStrategy]
